%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------


\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman


\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.8]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name


%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Emma} % Your first name
\familyname{Tosch} % Your last name

% All information in this block is optional, comment out any lines you don't need
%\title{Curriculum Vitae}
\address{E456 Innovation Hall}{Burlington, VT}
\email{Emma.Tosch@uvm.edu}
\homepage{https://uvm.edu/~etosch} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\homepage{https://sites.google.com/view/sikka-anmol/home}{Homepage}
%\extrainfo{DOB: September 15, 1997}
%\photo[70pt][0.4pt]{pictures/House} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}
%----------------------------------------------------------------------------------------
\newcommand{\cics}{College of Information and Computer Sciences}
\newcommand{\umass}{University of Massachusetts Amherst}
\newcommand{\cems}{College of Engineering and Mathematical Sciences}
\newcommand{\uvm}{University of Vermont}
\newcommand{\me}{\emph{Emma Tosch}}

\begin{document}

\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{Research Interests}
The research questions that motivate me relate to supporting sound experimental methodologies within complex software systems. I use methods from  domain-specific programming language design to build languages and tools for data scientists and social scientists.

\section{Education}
% cventry has 6 arguments
\cventry{Sep. 2020}{PhD}
 {\textbf{Computer Science}}
 {}
 {\umass{}}
 {Thesis: System Design for Digital Experiments\\Advisors: Profs. David Jensen and J. Eliot B. Moss}

% \cventry{Feb. 2015}{MS}
%  {\textbf{Computer Science}}
%  {}
%  {\umass{}}
%  {}

\cventry{May 2011}{MA}{\textbf{Computer Science}}{}{Brandeis University}{Note: Part of a combined post-baccalaureate and MA program in computer science.}

\cventry{Jun. 2008}{BA}{\textbf{English Literature}}{}{Wellesley College}{}


\section{Academic Appointments}
%% \cventry{Jul. 2020 -- present}{Research Affiliate}
%% {\cems{}, \uvm{}}{Temporary research affiliation until January 2021}{}{}
\cventry{Jan. 2021--\\present}{Assistant Professor}
 {\cems{}, \uvm{}}{}{}{}
\cventry{May 2018 -- Aug. 2020}{Research Assistant}
 {\umass{}}
 {Knowledge Discovery Lab}
 {Supervisor: David Jensen}
 {Developed tools and methods to evaluate autonomous black-box agents for the DARPA Explainable AI (XAI) program.}
 
\cventry{May 2013 -- Dec. 2016}{Research Assistant}
 {\umass{}}
 {PLASMA Lab}
 {Supervisor: Emery Berger}
 {Developed a domain specific programming language and runtime system to design, debug, and deploy scientific surveys on the web, at scale.}
 
   \cventry{Sep. 2011 -- Jan. 2013}{Research Assistant}
  {\umass{}}
  {Computational Intelligence Lab}
  {Supervisor: Lee Spector}
  {Devised a new measure for evaluating parameters of evolutionary search based on techniques from nonparametric statistics.}
  

\section{Publications}
\cventry{\emph{In submission}}
        {Stick it to the Man: Correcting for the Adversarial Behavior of Subjects in Experiments on Social Networks}
        {}
        {}
        {Kaleigh Clary, \me{}, Jeremiah Onaolapo, David D. Jensen}
        {}
        {}
\cventry{\emph{In submission}}
        {Toward Counterfactual Explanation of Agent Behavior in Dynamic and Relational Environments}
        {}
        {}
        {\me{}, Kaleigh Clary, David D. Jensen}
        {}
        {}
\cventry{\emph{In submission}}
        {Measuring and Characterizing Generalization in Deep Reinforcement Learning}
        {}
        {}
        {Sam Witty, Jun Ki Lee, \me{}, Akanksha Atrey, Kaleigh Clary, Michael L. Littman, David D. Jensen}
        {}
        {}          
          %\subsection{Refereed Conferences and Workshops}
\cventry{OOPSLA 2019}
        {PlanAlyzer: Assessing Threats to the Validity of Online Experiments}
        {}
        {Proceedings of the 2019 ACM International Conference on Object Oriented Programming Systems Languages and Applications}
  {\me{}, Eytan Bakshy, Emery Berger, David D. Jensen, J. Eliot B. Moss}
  {\textbf{Selected as a SIGPLAN research highlight and a CACM research highlight.}}
\cventry{NeurIPS Workshop 2018}
        {ToyBox: Better Atari Environments for Testing Reinforcement Learning Agents}
        {}
        {Systems for Machine Learning Workshop at the 32nd Conference on Neural Information Processing Systems}
        {John Foley,* \me{},* Kaleigh Clary, David D. Jensen}
        {}
        {}
\cventry{NeurIPS Workshop 2018}
        {Measuring and Characterizing Generalization in Deep Reinforcement Learning}
        {}
        {Critiquing and Correcting Trends in Reinforcement Learning Workshop at the 32nd Conference on Neural Information Processing Systems}
        {Sam Witty, Jun Ki Lee, \me{}, Akanksha Atrey, Michael Littman, David D. Jensen}
        {}
        {}
\cventry{NeurIPS Workshop 2018}
        {Let's Play Again: Variability of Deep Reinforcement Learning Agents in Atari Environments}
        {}
        {Critiquing and Correcting Trends in Reinforcement Learning Workshop at the 32nd Conference on Neural Information Processing Systems}
        {Kaleigh Clary, \me{}, John Foley, David D. Jensen}
        {}
        {}
\cventry{CODE 2015}
        {Formal Verification and Automated Causal Inference for Internet-Scale Experiments}
        {}
        {Conference on Digital Experimentation}
        {\me{}, E. Bakshy}
        {}
        {}
\cventry{OOPSLA 2014}
        {SurveyMan: Programming and Debugging Surveys at Scale}
        {}
        {Proceedings of the 2014 ACM International Conference on Object Oriented Programming Systems Languages and Applications}
        {\me{}, E. Berger} 
        {\textbf{Best Paper Award}}
        {}
  
\cventry{GECCO Workshop 2012}
        {Achieving COSMOS: A metric for determining when to give up and when to reach for the stars}
        {}
        {Proceedings of the 14th International Conference on Genetic and Evolutionary Computation Conference Companion}
        {\me{}, L. Spector}
        {}
        {}
  
\cventry{ICCS 2011}
        {Compositional Autoconstructive Dynamics}
        {}
        {Proceedings of the 8th International Conference on Complex Systems}
        {Kyle I. Harrington, \me{}, Lee Spector, Jordan Pollack}
        {}
        {}
\cventry{FLAIRS 2011}
        {Evaluating Conversational Characters Created through Question Generation}
        {}
        {Proceedings of the 24th International Florida Artificial Intelligence Research Society Conference}
        {Grace Chen, \me{}, Ron Artstein, Anton Leuski, David Traum}
        {}
        {}

\section{Industrial Research Experience}

 \cventry{Summer 2015}{Research Intern}
 {Facebook, Inc. Menlo Park, CA}
 {Core Data Science -- Economic Research Team, Statistics and Decision Science Team}
 {Supervisor: Eytan Bakshy}
 {Static Analysis for the PlanOut DSL}
 

  \cventry{Summer 2010}{Research Intern}
  {Institute for Creative Technologies. Playa Vista, CA}
  {}
  {Supervisor: Ron Artstein}
  {Natural language generation and question-answering system for virtual humans}




\section{Honors, Scholarships, and Awards}
  2021~CACM Research Highlight\\
  2020~SIGPLAN Research Highlight\\
  2015~WPI STEM Faculty Launch participant and travel grant\\
  2015~NCWIT Symantec Student Seed Funding (for UMass CS Women)\\
 2015~UMass Amherst School of Computer Science Outstanding Synthesis Award\\
  2014~OOPSLA Best Paper Award\\
  2014~PLDI ACM Student Research Competition (1st Place)\\
  2013~Future of Software Engineering Symposium Scholarship at Microsoft Research\\
  2013~Programming Languages Mentoring Workshop Scholarship\\
  2012~ACM-W conference scholarship (attended SIG-EVO)\\
  2010~Grace Hopper Celebration of Women in Computing Scholarship\\
  2005~Humanities Foundation Award in English Literature\\


  \section{Teaching Experience}

  \cventry{Fall 2021}
          {Instructor}
          {System Design for Knowledge Discovery}
          {\uvm{}}
          {Upper Undergraduate/Graduate}
          {}

\cventry{Spring 2021}
  {Instructor}
  {Reinforcement Learning}
  {\uvm{}}
  {Upper Undergraduate/Graduate}
  {}

\cventry{Spring 2018}
    {Instructor}
    {Reasoning Under Uncertainty}
    {\umass{}}
    {Undergraduate}
    {Co-taught with Luis Pineda}

\cventry
{Fall 2017}
{Teaching Assistant}
    {Advanced Logic}
    {\umass{}}
    {Upper Undergraduate/Graduate}
    {Taught by Prof. Neil Immerman}
    

\cventry
    {Spring 2017\\ Spring 2013}
{Teaching Assistant, Guest Lecturer}
    {Reasoning Under Uncertainty}
    {\umass{}}
    {Undergraduate}
    {Taught by Prof. Andrew McGregor}
    

    \cventry{Spring 2011}
    {Teaching Assistant, Guest Lecturer}
    {Introduction to Theory of Computation}
    {Brandeis University}
    {Undergraduate}
    {Taught by Dr. Antonella DiLillo}

    \cventry{Fall 2010}
    {Teaching Assistant}
    {Structure and Interpretation of Computer Programs}
    {Brandeis University}
    {Undergraduate}
    {Taught by Prof. Harry Mairson}
    
    \cventry{Spring 2010}
    {Teaching Assistant}
    {Data Structures}
    {Brandeis University}
    {Undergraduate}
    {Taught by Dr. Antonella DiLillo}

\section{Advising and Mentoring Experience}
  
    \cventry    
    {Summer 2016}
{Mentor}
    {Project on detecting adversarial behavior amongst online survey-takers}
    {Rosario Huamani Carpio, Pomona College, B.A.  2018}
    {}
    {REU Program, PLASMA Lab, University of Massachusetts Amherst}

\cventry{Summer 2015}
{Mentor}
    {Project for developing a SurveyMan graphical interface in React}
    {Prakhar Srivastav, Columbia University, M.S. 2016}
    {}
    {Google Summer of Code, PLASMA Lab, University of Massachusetts Amherst}
    

\cventry{Summer 2013\\ Spring 2014}
{Mentor}
    {Early-stage research project on developing tools for writing sound online surveys}
    {Molly McMahon, \umass{}, B.A. 2015}
    {}
    {REU Program \& Independent Study, PLASMA Lab, University of Massachusetts Amherst}
    



% \section{Teaching Training}
% Fall 2015.~~Active Learning Training with Rachel Rybaczuk.\\
% Fall 2015.~~CIRTL Course.  Diversity in College Classroom:  Teaching the STEM Undergraduate.


\section{Other Work Experience}

\cventry{May 2017 -- Aug. 2017}
 {Project Assistant}  
 {\umass{}} 
 {Prof. Charles Weems}
 {Amherst, MA}
 {}
\cventry{Sep. 2014 -- Dec. 2014}
{Software Engineering Intern} 
{Google, Inc.}
{}
{Mountain View, CA}
{}

\cventry{Mar. 2008 -- May 2009}
{Data Warehouse Analyst} 
{Recombinant Data Corp.}
{}
{Newton, MA}
{}
%  {\bf Usher}. September 2006 -- May 2008. American Repertory Theater. Cambridge, MA.\\ % comment this out later
%\item[Assistant Loan Processor.] June 2005 -- October 2006. Hoffman Companies. Brookline, MA.
%  {\bf Clerk}. May 2006 -- August 2006. Lulu's Bakery. Boston, MA.\\ % comment this out later
%  {\bf Laborer}. January 2006 -- May 2006. Natick Community Organic Farm. Natick, MA.\\ % comment this out later
%\item[Intern.] June 2004 -- August 2004. New Jersey Division of Law and Public Service. Trenton, NJ.
%  {\bf Clerk}. June 2002 -- April 2003. Wawa (Convenience Store). Hamilton, NJ.\\ % comment this out later

\section{Selected Talks and Presentations}

\subsection{Programming Languages and Experimentation}
\cventry{23 Oct. 2019}{Oral Presentation (full)}{OOPSLA 2019}{Athens, Greece}{}{}
\cventry{9 Dec. 2016}{Invited talk}{Wellesley College}{Wellesley, MA}{}{}
\cventry{31 May 2016}{Oral presentation (full)}{NEPLS Spring 2016}{Amherst, MA}{}{}
\cventry{17 Oct. 2015}{Poster presentation}{CODE@MIT}{Cambridge, MA}{}{}

\subsection{Software Infrastructure for Machine Learning}
\cventry{7 Dec. 2018}{Poster presentation}{NeurIPS Systems for ML Workshop}{Montreal, QC}{}{}
\cventry{4 Oct. 2018}{Oral presentation (full)} {IBM AI Systems Day}{Cambridge, MA}{}{}


\subsection{Programming and Debugging Surveys}
\cventry{8 Nov. 2016}{Invited talk}{SPLASH-I}{Amsterdam, Netherlands}{}{}
\cventry{1 Oct. 2015}{Invited talk}{Union College}{Schenectady, NY}{}{}
\cventry{13 May 2015}{Invited talk}{Google, Inc.}{Cambridge, MA}{}{}
\cventry{22 Oct. 2014}{Oral pressentation (full)}{OOPSLA 2014}{Portland, OR}{}{}
\cventry{11 Jun. 2014}{Oral presentation (short)}{PLDI Student Research Competition}{Edinburgh, Scotland}{}{}
\cventry{25 Jan. 2014}{Oral presentation (full)}{POPL OBT Workshop}{San Diego, CA}{}{}

\subsection{Detecting Convergence in Population-based Genetic Programming Methods}
    \cventry{7 July 2012}{Oral presentation (full)} {GECCO Understanding Problems Workshop}{Philadelphia, PA}{}{}
    
    \subsection{General Non-technical Topics in Computing}
\cventry{22 Oct. 2019}{Panelist}{Programming Languages Mentoring Workshop}{Athens, Greece}{}{}
\cventry{23 Jun. 2019}{Panelist}{Programming Languages Mentoring Workshop}{Phoenix, AZ}{}{}
\cventry{24 Apr. 2015}{Panelist}{MassMutual Women in Technology Conference}{Springfield, MA}{}{}


\section{Professional Activities and Service}
\cventry{2021}{Reviewer}{Dynamic Languages Symposium (DLS) Review Committee}{}{}{}
\cventry{2021}{Reviewer}{OOPSLA External Review Committee}{}{}{}
\cventry{2021}{Reviewer}{$\langle$Programming$\rangle$ Volume~6 Review Committee}{}{}{}
\cventry{2020}{Organizer}{Virtual PhD recruiting}{\url{https://phd-recruiting.com}}{}{}
\cventry{2020}{Volunteer}{Arizona Voter Protection}{}{}{}
\cventry{2019}{Evaluator}{SLE Artifact Evaluation Committee}{}{}{}
\cventry{2018}{Evaluator}{ECOOP Artifact Evaluation Committee}{}{}{}{}
\cventry{Jan. 2016 -- Jan. 2017}{Graduate Representative}{\umass{}, \cics{} Faculty}{}{}{}
\cventry{2016}{Student Volunteer}{PLDI Conference}{}{}{}
\cventry{Jun. 2016 -- Jan. 2017}{Webmaster}{CS Women}{\umass{}, \cics{}}{}{}
\cventry{Jan. 2016 -- May 2016}{Treasurer}{UMass CS Women}{\umass{}, \cics{}}{}{}
\cventry{Jan. 2015 -- Jan. 2016}{Co-Chair}{UMass CS Women}{\umass{}, \cics{}}{}{}
\cventry{2016}{Reviewer}{PLDI External Review Committee}{}{}{}{}
\cventry{2016}{Reviewer}{ECOOP External Review Committee}{}{}{}
\cventry{2016}{Reviewer}{POPL OBT Workshop Program Committee}{}{}{}
\cventry{2015}{Participant}{WPI STEM Faculty Launch}{}{}{}
\cventry{2015}{Participant}{ACM-W Early Career Mentoring Workshop}{}{}{}
\cventry{2016}{Reviewer}{ECOOP DSLDI Workshop Program Committee}{}{}{}
\cventry{2016}{Evaluator}{PLDI Artifact Evaluation Committee}{}{}{}
\cventry{2014}{Reviewer}{NCWIT Aspirations Scholarship}{}{}{}
\cventry{2015}{Reviewer}{POPL Artifact Evaluation Committee}{}{}{}
\cventry{2014}{Student Volunteer}{SPLASH Conference}{}{}{}
\cventry{Sep. 2011 -- May 2014}{Steward}{Graduate Employee Organization, UAW 2322}{\umass{}}{}{}
\end{document}



